---
title: "Manhattan Borough - Housing Sale Prices"
author: "Robert Flamenbaum, Samira Zarandioon, Patrick McDevitt"
date: "22 fév 2017"
#knit : (function(inputFile,encoding){
#			rmarkdown::render(inputFile,
#			encoding=encoding,
#			output_file=file.path(dirname(inputFile),out_dir,'data_clean.html')})

output: 
  html_document: 
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

### Data Cleaning

```{r nyc housing, echo=FALSE, message = FALSE}

# Author: Benjamin Reddy
# Taken from pages 49-50 of O'Neil and Schutt

# ...	-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
# ...	modifications added by patrick mcdevitt, 25-fev-2017
# ...	-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-

#require(gdata)
#require(plyr) #Added by Monnie McGee
#install the gdata and plyr packages and load in to R.
library(plyr)
library(gdata)
library(stringr)
library(knitr)
library(markdown)

# ... clean up workspace

rm(list=ls())

# ...	-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
# ...	identify some directories for output
# ...	-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-

home_dir <- "/home/mcdevitt/_smu/msds 6306 - data science/semaine 6/lsa_28feb"
data_dir <- "./data"
analysis_dir <- "./analysis"
paper_dir <- "./paper"

setwd(home_dir)
setwd(data_dir)

```

-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  
__Ph I - Create quality data set to support analysis__  
-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  

First steps ...  
- read in .csv file of Manhattan Borough property sale prices  
- change names of any variables that begins with digits  
- convert variable names to lower case  
- do some initial data exploration to identify outliers, useful transformations  

  
-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  


```{r echo=FALSE, message = FALSE}
# ...	-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
# ...	read in .csv file of manhattan sale prices
# ...	-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-

sales_data_filename <- "rollingsales_manhattan.csv"
bk <- read.csv(paste0(sales_data_filename),
			   skip = 4,
			   header = TRUE,
			   stringsAsFactors = FALSE)

# ...	-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
# ...	evalaute data and clean
# ...	-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-

#head(bk)
#summary(bk)
#str(bk)

## clean/format the data with regular expressions
## More on these later. For now, know that the
## pattern "[^[:digit:]]" refers to members of the variable name that
## start with digits. We use the gsub command to replace them with a blank space.
# We create a new variable that is a "clean' version of sale.price.
# And sale.price.n is numeric, not a factor.

bk$SALE.PRICE.N <- as.numeric(gsub("[^[:digit:]]","", bk$SALE.PRICE))
count(is.na(bk$SALE.PRICE.N))

# make all variable names lower case
names(bk) <- tolower(names(bk)) 

## Get rid of leading digits
bk$gross.sqft <- as.numeric(gsub("[^[:digit:]]","", bk$gross.square.feet))
bk$land.sqft <- as.numeric(gsub("[^[:digit:]]","", bk$land.square.feet))
bk$year.built <- as.numeric(as.character(bk$year.built))

# ...	-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
# ...	setwd() to .data directory to store some cleanign/exploration plots
# ...	-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-

## do a bit of exploration to make sure there's not anything
## weird going on with sale prices

```



-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  
__Histogram of Raw Data Set__  
-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  


```{r echo=FALSE, message = FALSE}

attach(bk)
hist(sale.price.n) 
detach(bk)

## keep only the actual sales

bk.sale <- bk[bk$sale.price.n != 0,]


```

-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  
__Scatter Plots of Sq-Ft vs. Sale Price__  
-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  


```{r echo=FALSE, message = FALSE}

plot(bk.sale$gross.sqft, bk.sale$sale.price.n)

plot(log10(bk.sale$gross.sqft), log10(bk.sale$sale.price.n))

## for now, let's look at 1-, 2-, and 3-family homes

bk.homes <- bk.sale[which(grepl("FAMILY", bk.sale$building.class.category)),]
dim(bk.homes)

plot(log10(bk.homes$gross.sqft), log10(bk.homes$sale.price.n))

summary(bk.homes[which(bk.homes$sale.price.n < 100000),])

## remove outliers that seem like they weren't actual sales
bk.homes$outliers <- (log10(bk.homes$sale.price.n) <= 5) + 0
bk.homes <- bk.homes[which(bk.homes$outliers == 0),]

```


-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  
__After subsetting to 1,2,3 unit homes, removing outliers, and transform to log price__  
-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  

- data set sufficiently cleaned and subsetted to support analysis of Manhattan housing prices   


```{r echo=FALSE, message = FALSE}

plot(log10(bk.homes$gross.sqft),log10(bk.homes$sale.price.n))
```

-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  
__Analysis data set definition__  
-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  

```{r echo=FALSE, message = FALSE}
str(bk.homes)


# ... -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
# ...		END_OF_FILE
# ... -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
```






```{r echo=FALSE, message = FALSE}

#output_html <- "cleaning.html"
#knit_interim <- "cleaning.md"
#knit_pattern <- str_c(home_dir, "/", "data_cleaning.Rmd")
#knit(knit_pattern) 
#markdownToHTML(file = knit_interim, output=output_html)

# ...	-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
# ...	do some analysis of the cleaned / subsetted / transformed data
# ...	-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-

setwd(home_dir)
setwd(analysis_dir)

bk.homes$log_price <- log10(bk.homes$sale.price.n)
bk.homes$dates <- as.Date(bk.homes$sale.date, "%m/%d/%Y")

iplt <- 1
iplt <- iplt + 1
png(filename = paste0("plot_", iplt, ".png"))
boxplot(log10(sale.price.n) ~ zip.code, data = bk.homes)
dev.off()

iplt <- iplt + 1
png(filename = paste0("plot_", iplt, ".png"))
boxplot(log10(sale.price.n) ~ neighborhood, data = bk.homes)
dev.off()

iplt <- iplt + 1
png(filename = paste0("plot_", iplt, ".png"))
boxplot(log10(sale.price.n) ~ total.units, data = bk.homes)
dev.off()

iplt <- iplt + 1
png(filename = paste0("plot_", iplt, ".png"))
boxplot(log10(sale.price.n) ~ tax.class.at.present, data = bk.homes)
dev.off()

by_zip <- ddply(bk.homes, c("neighborhood"), summarise,
               N    = sum(!is.na(log_price)),
               mean = mean(log_price, na.rm=TRUE),
               sd   = sd(log_price, na.rm=TRUE),
               se   = sd / sqrt(N)
)


iplt <- iplt + 1
png(filename = paste0("plot_", iplt, ".png"))
plot(log_price ~ dates, data = bk.homes, col = "blue")
abline(lm(log_price ~ dates, data = bk.homes), col = "black", lty = 3, lwd = 3)
dev.off()

```
