---
title: "analysis - manhattan"
author: "Robert Flamenbaum, Samira Zarandioon, Patrick McDevitt"
date: "27 février 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Manhattan Project

Some initial analysis to evalaute housing trend prices in relation to fundamental characteristics :  
- property square footage  
- zip code & neighborhood  
- number of units in building  


```{r manhattan.proj, echo = FALSE, message = FALSE}

library(plyr)
library(gdata)
library(stringr)
library(knitr)
library(markdown)

# ...	-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
# ...	load the cleaned data set from ../data/ directory ...
# ...	-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-

data_dir <- "../data"
Rda_dataset_name <- "manhattan.proj.Rda"

load(paste0(data_dir, "/", Rda_dataset_name))

# ...	-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
# ...	do some analysis of the cleaned / subsetted / transformed data
# ...	-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-

bk.homes$log_price <- log10(bk.homes$sale.price.n)
bk.homes$dates <- as.Date(bk.homes$sale.date, "%m/%d/%Y")

```

-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  
__BoxPlot of sale price vs. Zip Code__  
-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  


```{r echo = FALSE, message = FALSE}

boxplot(log10(sale.price.n) ~ zip.code, data = bk.homes)
```

-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  
__BoxPlot of sale price vs. Neighborhood__  
-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  

```{r echo = FALSE, message = FALSE}
boxplot(log10(sale.price.n) ~ neighborhood, data = bk.homes)
```
-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  
__BoxPlot of sale price vs. Total Units__  
-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  

```{r echo = FALSE, message = FALSE}
boxplot(log10(sale.price.n) ~ total.units, data = bk.homes)
```


-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  
__BoxPlot of sale price vs. Tax Classification__  
-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  

```{r echo = FALSE, message = FALSE}
boxplot(log10(sale.price.n) ~ tax.class.at.present, data = bk.homes)
```


```{r echo = FALSE, message = FALSE}
by_zip <- ddply(bk.homes, c("neighborhood"), summarise,
               N    = sum(!is.na(log_price)),
               mean = mean(log_price, na.rm=TRUE),
               sd   = sd(log_price, na.rm=TRUE),
               se   = sd / sqrt(N) )
```


-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  
__Trend plot vs. sale date - no obvious trend here__  
-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-  

```{r echo = FALSE, message = FALSE}
plot(log_price ~ dates, data = bk.homes, col = "blue")
abline(lm(log_price ~ dates, data = bk.homes), col = "black", lty = 3, lwd = 3)


# ... -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
# ...		END_OF_FILE
# ... -=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-
```

